---
title: "Shiny Application and Reproducible Pitch"
author: "FrockyG"
date: "2025-03-14"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Project Goal

This peer assessed assignment has two parts.

First, you will create a Shiny application and deploy it on Rstudio’s servers.

Second, you will use Slidify or Rstudio Presenter to prepare a reproducible pitch presentation about your application.

## Steps to Perform

- Write a shiny application with associated supporting documentation. The documentation should be thought of as whatever a user will need to get started using your application.
- Deploy the application on Rstudio’s shiny server
- Share the application link by pasting it into the provided text box
- Share your server.R and ui.R code on github

## How to use the application

This application fits two linear models using the data from the R pressure dataset.

- Model 1 is a 1-factor linear model of $pressure$ as a function of $temperature$;
- Model 2 is a 1-factor linear model of $pressure$ where the dependent variable is the spline function: $max(temperature-250,0)$.

As can be seen in the server application available in [shinyapps](https://frockyg.shinyapps.io/dp-week-4/), Model 2 results in a better model fit than Model 1.

The data used, ui.R and Server.R code are available in this [github repo](https://github.com/frockyg/DP-Week-4).

## Vapor Pressure of Mercury as a Function of Temperature
The dataset used in the Shiny application is the pressure dataset in R displayed in the plot below.  
```{r pressure}
plot(pressure)
```

